A Large and Variable Leading Tail of Helium in a Hot Saturn Undergoing Runaway Inflation

### 2023-12-04 paper/paper1/ms.tex
Make the repository public and put a link to the repo in the paper.
Comparison to CARMENES data, section 6.4

@@

>>>>

\authorcomment1{The entire suite of project files, reproducible Jupyter Notebooks, selected data files, and revision history are publically available as a reproducible GitHub repository\footnote{\url{https://github.com/BrownDwarf/disperse}}.}

@@

\subsection{Comparison to CARMENES detection}
\authorcomment1{Recently, \citet{2023AJ....166...69B} reported the transmission spectrum of HAT-P-67~b using the CARMENES spectrograph \citep{2014SPIE.9147E..1FQ}.  The point-and-stare observations were scheduled to coincide with transits, providing relatively short $<1$ hour out-of-transit baselines on either side of the transit.  The CARMENES team detected variable \ion{He}{1} 10830 absorption, but could not uniquely attribute the variability to an exoplanet origin owing to the limited orbital phase coverage.  The CARMENES visible channel spectrograph also covers H$\alpha$, which yielded a significant detection of Hydrogen variability through the exoplanet transit.  The CARMENES team also detected \ion{Ca}{2} IRT and \ion{Na}{1} via cross-correlation spectroscopy, consistent with an exoplanet atmosphere origin.  Our analysis of the \ion{Ca}{2} IRT showed much less conspicuous variability compared to the \ion{He}{1} 10830 lines, but still some hint of variability (\emph{c.f.} Figure \ref{fig:CaPhaseScan}).  A joint analysis of both the CARMENES and HPF data may help to paint a more complete picture of these variable signals.
}
